Intergroup contact fosters\\more inclusive social identities\thanks{Reimer, N. K., Kamble, S. V., Schmid, K., \& Hewstone, M. (in press). Intergroup contact fosters more inclusive social identities. \textit{Group Processes \& Intergroup Relations.}}

### 2020-08-31 manuscript/manuscript.tex
in press

\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}

% Font
\usepackage{MinionPro}
\input glyphtounicode
\pdfgentounicode=1
\usepackage{microtype}
\usepackage[super]{nth}
\usepackage{csquotes}

% Format
\setlength{\parindent}{0.5in}
\setcounter{secnumdepth}{0}

% Language
\usepackage[american]{babel}

% Links
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black]{hyperref}

% Figures
\usepackage{graphicx}
\usepackage[small, labelfont=it, labelsep=period]{caption}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}

% References
\usepackage[style=apa]{biblatex}
\DeclareSourcemap{
  \maps[datatype=bibtex]{
    \map{
      \pertype{book}
      \step[fieldset=location, null]
      \step[fieldset=address, null]
    }
    \map{
      \pertype{incollection}
      \step[fieldset=location, null]
      \step[fieldset=address, null]
    }
  }
}
\addbibresource{references.bib}
\renewcommand*{\bibfont}{\small}

% Frontmatter
\title{Intergroup contact fosters\\more inclusive social identities\thanks{Reimer, N. K., Kamble, S. V., Schmid, K., \& Hewstone, M. (in press). Intergroup contact fosters more inclusive social identities. \textit{Group Processes \& Intergroup Relations}. \href{https://doi.org/10.31234/osf.io/zcgwt}{https://doi.org/10.31234/osf.io/zcgwt}}}
\date{April 6, 2020}

@@

\begin{abstract}
\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities. South Indian participants ($N = 351$) from diverse caste backgrounds viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships (caste, religion, nationality). Participants judged each person as “us” or “not us”, showing whom they included in their ingroup, and whom they excluded. Participants tended to exclude caste and religious minorities, replicating persistent social divides. Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more positive relations between an advantaged, an intermediate, and a disadvantaged caste group. Negative contact was associated with less inclusive identities. Contact and identity processes, however, did not affect entrenched opposition to (or undermine support for) affirmative action in advantaged and disadvantaged groups.\\[1ex]
\noindent {\footnotesize \textbf{Keywords:} intergroup contact, social identity, multiple categorization, intergroup relations, interminority relations, perceived discrimination, affirmative action}
\end{abstract}

\noindent How we feel about and act toward others depends on whom we consider “us” and “them”---that is, whom we include in, and exclude from, our ingroup (for a review, see \nptextcite{reimer_self-categorization_2020}).  In some situations, this distinction rests on one salient categorization, for example, someone's nationality at an international border. In diverse societies, however, this distinction often depends on multiple, overlapping group memberships. Individuals differ in how they construct their ingroup from these group memberships. Some espouse narrow definitions of who is “us” and “them”, while others adopt more inclusive identities. Many Americans, for example, associate being American with being White American \parencite{devos_american_2005}. This suggests that whom Americans consider “us” and “them” might depend on someone's race \emph{and} nationality. In this paper, we examine how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities. We use a novel method to study social identification across multiple social categories and to examine possible antecedents (intergroup contact, social dominance orientation) and consequences (intergroup attitudes, intergroup threat, support for affirmative action) of more inclusive identities.

\begin{figure*}
\centering
\includegraphics[scale=1]{../figures/figure-1}
\caption{
Schematic representations of social identity structures \protect\parencite{roccas_social_2002}, ordered by their social identity inclusiveness \protect\parencite{van_dommelen_construing_2015}. Shaded regions represent the groups which a participant has to categorize as “us” to be assigned that structure. An Indian Hindu, for example, might consider only people who share their nationality, religion, and caste as ingroup members (\emph{intersection}). Someone else might consider all their fellow Indians, whatever their religion or caste, as ingroup members (\emph{dominance}). Another person might consider anyone who shares their nationality or religion as ingroup members (\emph{merger}).
}
\label{fig:f1}
\end{figure*}

Social psychologists highlighted the importance of considering two \parencite{berry_immigration_1997, crisp_multiple_2007, dovidio_commonality_2009} or more \parencite{roccas_social_2002} social categories for understanding intergroup relations. \textcite{crisp_multiple_2007} reviewed evidence that we tend to have more favourable attitudes towards people with whom we share some, but not all, group memberships than towards people with whom we do not share any group memberships. \textcite{gaertner_reducing_2000} showed that espousing a more inclusive common ingroup identity (e.g., Indian) over a narrower identity (e.g., Hindu, Muslim) can extend the benefits of ingroup favouritism to outgroup members and thus reduce intergroup bias. \textcite{roccas_social_2002} recognized that, though we all hold multiple overlapping group memberships, we differ in how we construct our social identities from these group memberships. Broadly, these perspectives recognize that we are part of multiple overlapping groups; that we use these group memberships to construct a subjective sense of who is “us” and “them”; and that espousing more inclusive social identities can reduce prejudice and discrimination.

Diverse societies confront their members with the decision of which intersections of various group memberships to include in their subjective ingroup. One Indian Hindu, for example, might constrict their ingroup to people of the same nationality, religion, and caste. Another Indian Hindu might consider all Indians, whatever their religion or caste, as ingroup members (see Figure~\ref{fig:f1}). Past research \parencite{van_dommelen_construing_2015} indeed observed substantial individual differences in whom participants considered “us” and “not us”. Some participants espoused more inclusive social identities---that is, they included more people in their subjective ingroup. Other participants espoused less inclusive social identities---that is, they included fewer people in their subjective ingroup. All participants, however, belonged to the same disadvantaged minority group. Past research thus provided evidence for individual differences, but did not examine group differences in whom people consider “us” and “not us”.

>>>>

\documentclass[12pt, a4paper]{article}

% Font
\usepackage[utf8]{inputenc}
\usepackage{MinionPro} 
\input{glyphtounicode}
\pdfgentounicode=1 
\usepackage{microtype}
\usepackage[super]{nth}

 % Format
\setlength{\parindent}{0.5in}
\setcounter{secnumdepth}{0}
\usepackage{authblk}
\renewcommand\Affilfont{\small}
\usepackage[hang, flushmargin]{footmisc}

% Language
\usepackage[british]{babel}

% Links
\usepackage[colorlinks = true, linkcolor = black, urlcolor = black, citecolor = black]{hyperref}

% Figures
\usepackage{graphicx}
\usepackage[small, labelfont = bf, labelsep = newline]{caption}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage[table, xcdraw]{xcolor}

% References
\usepackage{csquotes}
\usepackage[style = apa]{biblatex}
\addbibresource{references.bib}

% Frontmatter
\title{Intergroup contact fosters\\more inclusive social identities\thanks{Reimer, N. K., Kamble, S. V., Schmid, K., \& Hewstone, M. (in press). Intergroup contact fosters more inclusive social identities. \textit{Group Processes \& Intergroup Relations.}}}
\author[1]{Nils Karl Reimer}
\author[2]{Shanmukh V. Kamble}
\author[3]{Katharina Schmid}
\author[1]{Miles Hewstone}
\affil[1]{University of Oxford, United Kingdom}
\affil[2]{Karnatak University Dharwad, India}
\affil[3]{Universitat Ramon Llull, ESADE Business School, Spain}
\date{June 25, 2020}

@@

\begin{abstract}
\noindent We examined how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities. South Indian participants ($N = 351$) from diverse caste backgrounds viewed 24 identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships (caste, religion, nationality). Participants judged each person as “us” or “not us”, showing whom they included in their ingroup, and whom they excluded. Participants tended to exclude caste and religious minorities, replicating persistent social divides. Bridging these divides, cross-group friendship was associated with more inclusive identities which, in turn, were associated with more positive relations between an advantaged, an intermediate, and a disadvantaged caste group. Negative contact was associated with less inclusive identities. Contact and identity processes, however, did not affect entrenched opposition to (or undermine support for) affirmative action in advantaged and disadvantaged groups.\\[1ex]
\noindent \textbf{Keywords:} intergroup contact, social identity, multiple categorization, interminority relations, perceived discrimination, affirmative action \\[1ex]
\end{abstract}

\noindent How we feel about and act toward others depends on whom we consider “us” and “them”---that is, whom we include in, and exclude from, our ingroup \parencite[for a review, see][]{reimer_self-categorization_2020}. In some situations, this distinction rests on one salient categorization, for example, someone’s nationality at an international border. In diverse societies, however, this distinction often depends on multiple, overlapping group memberships. Individuals differ in how they construct their ingroup from these group memberships. Some espouse narrow definitions of who is “us” and “them”, while others adopt more inclusive identities. Many Americans, for example, associate being American with being White \parencite{devos_american_2005}. This suggests that whom Americans consider “us” and “them” might depend on someone’s race \emph{and} nationality. In this paper, we examine how people construct their social identities from multiple group memberships---and whether intergroup contact can reduce prejudice by fostering more inclusive social identities. We use a novel method to study social identification across multiple social categories and to examine possible antecedents (intergroup contact, social dominance orientation) and consequences (intergroup attitudes, support for affirmative action, intergroup threat) of more inclusive identities.

Social psychologists have highlighted the importance of considering two \parencite{berry_immigration_1997, crisp_multiple_2007, dovidio_commonality_2009} or more \parencite{roccas_social_2002} social categories for understanding intergroup relations. \textcite{crisp_multiple_2007} reviewed evidence that we tend to have more favourable attitudes towards people with whom we share some, but not all, group memberships than towards people with whom we do not share any group memberships. \textcite{gaertner_reducing_2000} showed that espousing a more inclusive common ingroup identity (e.g., Indian) over a narrower identity (e.g., Hindu) can extend the benefits of ingroup favouritism to outgroup members and thus reduce intergroup bias. \textcite{roccas_social_2002} recognized that, though we all hold multiple overlapping group memberships, we differ in how we construct our social identities from them. Broadly, these perspectives recognize that we belong to multiple overlapping groups; that we use these group memberships to construct a subjective sense of who is “us” and “them”; and that espousing more inclusive social identities can reduce prejudice and discrimination.

Diverse societies confront their members with the decision of which intersections of various group memberships to include in their ingroup. One Indian Hindu, for example, might restrict their ingroup to people of the same nationality, religion, and caste. Another Indian Hindu might consider all Indians, whatever their caste or religion, as ingroup members (Figure~\ref{fig:f1}). Past research \parencite{van_dommelen_construing_2015} indeed observed substantial individual differences in whom participants considered “us” and “not us”. Some participants espoused more inclusive social identities---that is, they included more people in their subjective ingroup. Other participants espoused less inclusive social identities---that is, they included fewer people in their subjective ingroup. All participants \parencite[studied by][]{van_dommelen_construing_2015}, however, belonged to the same disadvantaged minority group. Past research thus provided evidence for individual differences, but did not examine group differences in whom people consider “us” and “not us”.

\begin{figure}
\centering
\caption{
Schematic representations of social identity structures \protect\parencite{roccas_social_2002}, ordered by their social identity inclusiveness \protect\parencite{van_dommelen_construing_2015}
}
\includegraphics[scale=1]{../figures/figure-1}
\caption*{\textit{Note.} Shaded regions represent the groups which a participant has to categorize as “us” to be assigned that structure. An Indian Hindu, for example, might consider only people who share their nationality, religion, and caste as ingroup members (\emph{intersection}). Someone else might consider all their fellow Indians, whatever their religion or caste, as ingroup members (\emph{dominance}). Another person might consider anyone who shares their nationality or religion as ingroup members (\emph{merger}).}
\label{fig:f1}
\end{figure}

Group membership, however, often shapes whom people include in, and exclude from, their subjective ingroup. For majority-group members, negotiating their ethnic and national identities means something different than for minority-group members \parencite[for a review, see][]{dovidio_commonality_2009}. Majority-group members face the choice of including or excluding ethnic, religious, and other minorities from their subjective ingroup. Choosing to include or exclude minorities could, for example, reflect whether a majority-group member holds multicultural or nativist views. Minority-group members face the choice of aligning themselves with the dominant majority group or seeking a common ingroup identity with other minority groups. We expect that group differences are as great as, if not greater than, individual differences in social identity construals---especially if groups differ in status and power. Our research includes participants from advantaged, intermediate, and disadvantaged backgrounds to study how groups differ in terms of whom their members consider “us” and “not us”.

How we think and feel about others depends on whether we include them in our ingroup. Dividing others into “us” and “not us” is thus a necessary and sufficient condition for ingroup favouritism \parencite{tajfel_human_1981}. Past research has shown that people favour ingroup members in resource allocation \parencite{tajfel_social_1971}, in causal attribution \parencite{hewstone_ultimate_1990, taylor_ethnocentrism_1974}, in helping behaviour \parencite{levine_identity_2005}, in information processing \parencite{van_bavel_neural_2008}, and in evaluation \parencite{otten_evidence_2000}. Considering more people as “us” should extend ingroup favouritism to a wider range of people, and thus reduce prejudice and discrimination \parencite[for a review, see][]{nelson_common_2016}. Our research examines whether fostering more inclusive social identities leads to more favourable attitudes and less social distance toward national, religious, and caste outgroups.

Contact with members of other groups changes how we think and feel about them. Past research has shown that intergroup contact reduces prejudice \parencite{pettigrew_meta-analytic_2006} by decreasing intergroup anxiety, increasing empathy and perspective-taking, and by increasing knowledge about the other group \parencite{pettigrew_how_2008}. In addition, researchers have proposed that contact could reduce prejudice by changing how we see ourselves \parencite{pettigrew_generalized_1997, pettigrew_intergroup_1998}. Encountering diverse others could initiate a process of cognitive differentiation \parencite{kramer_social_2011} whereby individuals become aware of complex interrelations between their group memberships and adopt more complex social identities \parencite{schmid_antecedents_2009}---that is, they become aware that they belong to multiple categories and recognize that these multiple categories do not always overlap \parencite{van_dommelen_construing_2015}. Other research has found that intergroup contact can, under the right conditions, motivate people to adopt a more inclusive common ingroup identity \parencite{gaertner_contact_1994} and to include the outgroup in their self-concept \parencite{page-gould_understanding_2010}. If intergroup contact motivates people to adopt social identities that include outgroup members, it should reduce prejudice and discrimination against them. Our research examines whether intergroup contact can reduce prejudice against religious and caste outgroups by fostering social identities that include them as ingroup members.

Beyond prejudice, researchers have debated whether, by fostering more inclusive identities, intergroup contact helps or hinders social change. Social change often requires advantaged and disadvantaged groups to strive for redistributive policies. On the one hand, fostering inclusive identities could break down the boundaries between the advantaged ingroup and the disadvantaged outgroup---turning injustice faced by “them” into “our” problem. This process could narrow the gap between advantaged-group members’ support for the principle of equality and their opposition to its implementation \parencite{dixon_intergroup_2007}. On the other hand, fostering more inclusive identities could distract disadvantaged-group members from differences in resources and power, and thus reduce their demands for and support for social change \parencite{dixon_attitudes_2012, saguy_irony_2009}. Together, these mechanisms suggest that fostering more inclusive identities could increase support for social change among the advantaged, but decrease support among the disadvantaged. Our research examines how intergroup contact, by fostering more inclusive social identities, affects support for affirmative action policies, as well as perceptions of relative (dis-)advantage, in advantaged and disadvantaged groups.

Most research on intergroup relations examines relations between an advantaged majority group and a disadvantaged minority group. Most social contexts, however, feature various groups facing various disadvantages. \textcite{craig_coalition_2012} argued that racial minorities may respond to the disadvantages they face by derogating other racial minorities or by forming a coalition with them. They showed that perceiving discrimination can, as far as it fosters a shared ingroup identity with other disadvantaged groups, improve interminority relations. \textcite{vollhardt_inclusive_2016} observed that South Indians from disadvantaged caste and religious groups were more likely to express support for another disadvantaged group when they recognized similarities between their own and other groups’ experiences of discrimination. \textcite{dixon_contact_2017} found that Indian Muslims who reported having more contact with other disadvantaged groups were also more likely to recognize shared grievances and to express support for collective action benefiting all disadvantaged groups. Our research adds to this literature by examining intergroup relations between two disadvantaged groups, one of which occupies an intermediate position in the social hierarchy. We examine whether, by fostering shared ingroup identities, contact between disadvantaged groups can foster more positive intergroup relations, shared perceptions of disadvantage, and mutual support for affirmative action.

\subsection{Caste, Religion, Nation in South India}

We investigated these questions in the context of caste, religion, and nationality in South India. India provides an important context for studying social identification across multiple social categories. India is diverse. Indians belong to different castes, religions, and other groups that intersect in numerous ways. India is also underrepresented in psychological research.\footnote{Among the societies underrepresented in psychological research (Henrich et al., 2010), India is a prominent omission as it spans almost a fifth of the world’s population.} Few studies of intergroup relations \parencite[e.g.,][]{ghosh_hindu-muslim_1991, tausch_relationships_2009} focus on religious relations in India. Even fewer \parencite[e.g.,][]{cotterill_ideological_2014} focus on caste relations. Our research examined the cross-cutting categories of caste, religion, and nationality in a diverse sample of South Indian students.

Caste is a system of social relations that concentrates resources in the hands of dominant castes by restricting subordinate castes’ occupations and by enforcing segregation and endogamy \parencite{jodhka_caste_2012}. This system is underpinned by a tradition that conveys caste through markers such as surname and diet, ranks castes according to their supposed ritual purity, and condemns contact with supposedly less pure castes. This tradition includes the practice of untouchability which excludes some castes from public life and consigns them to landlessness and menial labour. Dalits, members of castes that have been subjected to untouchability, still face interpersonal discrimination and economic inequalities resulting from this (now illegal) practice. Since Independence, the Indian State has sought to redress caste-based injustices by reserving seats in state-run universities and state-sector jobs for ‘Scheduled Castes’ (the official term for Dalits) and ‘Scheduled Tribes’ (the official term for Adivasi, India’s indigenous peoples). Reservation policies, along with persistent discrimination, mean that caste identities continue to structure people’s lives.

Caste identities have different meanings for disadvantaged, advantaged, and intermediate groups. For the most disadvantaged, caste is often defined by their experience of discrimination and their resistance against it \parencite{jodhka_caste_2012}. Dalits have built movements to assert their economic and political rights---founding, for example, the Bahujan Samaj Party in 1984---and thus created a positive identity around their resistance against oppression. Dalits, however, often face violent backlash when asserting their rights \parencite[e.g.,][]{noauthor_15_2017}. For the most advantaged, Dalit emancipation threatens their social and economic dominance. Reservation policies, for example, restrict access to university seats for upper-caste applicants who must compete with all other applicants in the ‘General Merit’ category. Other groups occupy an intermediate position in the caste hierarchy. In 1990, the government extended reservations to ‘Other Backward Classes’, that is, communities that were socially and educationally disadvantaged, but had not been subjected to untouchability. For intermediate groups, caste is often defined by the question whether they can gain or maintain access to reserved university seats and government jobs. As a result, caste identities remain important in Indian politics.

South India is religiously diverse. In Karnataka, where we conducted this research, 84\% of inhabitants are Hindus, while 13\% are Muslims. Muslims face both structural inequalities and communal violence. In 2002, for example, over a thousand Muslims were killed in a pogrom in Gujarat \parencite{dhattiwala_political_2012}. In recent years, anti-Muslim violence has been increasing \parencite{amnesty_international_india:_2017}. Religion is intertwined with two currents of Indian nationalism \parencite{katz_hindu_2009}. On the one hand, the secular foundations of the Indian State resulted from an inclusive nationalism that strives to include Indians of all religions. On the other hand, Hindu nationalism (Hindutva) is an ideology that equates being Indian with being Hindu, thus excluding Muslims from the national identity. Narendra Modi’s Bharatiya Janata Party (BJP) government espouses Hindutva and enjoyed broad support at the time of our study \parencite{pew_research_center_three_2017}. Indians thus face a choice between two ideologies that either include Indian Muslims in the national identity or exclude them from it.

\subsection{Present research}

Our research used a novel method to study social identification across multiple categories in a sample of South Indians from diverse caste backgrounds. We examined how people construct their social identities from multiple group memberships, whether intergroup contact is associated with more inclusive social identities, and how more inclusive social identities relate to prejudice and support for social change. Below, we introduce the experimental task before reviewing our research questions and hypotheses.

We adapted the triple crossed-categorization task \parencite{van_dommelen_construing_2015} to assess how participants construct their social identities from multiple group memberships. In this task, participants view identity cards, each representing a person with whom participants shared none, one, two, or all of three group memberships. Participants report whether they consider each person as “us” or “not us”, showing whom they include in, or exclude from, their ingroup. This task allowed us to study identification across multiple social categories and how it relates to the predictors and outcomes in our hypotheses. Van Dommelen et al. \citeyear{van_dommelen_construing_2015} used a similar task to examine whom participants considered “us” and “not us”. However, their research included participants from only one group, aggregated participants’ categorizations into a single score, and tested whether that score correlated with aggregated responses to contact and attitude measures. Our research included participants from multiple groups and used multilevel modeling to test whether contact with and attitudes toward \emph{each} group were associated with the inclusion of \emph{that} group in one’s social identity. This allowed for a more fine-grained analysis of individual and group differences in identification across multiple social categories.

We pursued four research questions. First, we examined how participants’ group memberships shaped whom they included in, and excluded from, their ingroup (\emph{group differences}). We hypothesized that participants would exclude targets from religious and national outgroups---and that participants from advantaged castes would exclude targets from disadvantaged castes, and vice versa. We did not have a clear prediction for participants from intermediate backgrounds. Second, we examined whether past experiences with members of caste and religious outgroups shaped whom participants included in, and excluded from, their ingroup (\emph{individual differences}). We hypothesized that positive contact and cross-group friendship would be associated with more---and negative contact \parencite{barlow_contact_2012, hayward_toward_2017} with less---inclusive social identities. Third, we examined whether, by fostering more inclusive social identities, intergroup contact would be associated with less prejudice (\emph{intergroup attitudes}). We hypothesized that categorizing someone as “us” would be associated with more favourable attitudes and less social distance toward that person. Fourth, we examined how intergroup contact, by fostering more inclusive social identities, affects support for affirmative action in advantaged and disadvantaged groups (\emph{support for social change}). We hypothesized that more inclusive social identities would be associated with less perceived discrimination and less support for affirmative action among the disadvantaged, and with more perceived privilege and more support for affirmative action among the advantaged.

In addition, we explored how two other constructs related to more inclusive social identities. First, we examined ideological preferences for group dominance \parencite{sidanius_social_1999} as an additional predictor variable to rule out a potential confound, whereby people high in social dominance orientation might both eschew contact with caste and religious minorities and exclude them from the common ingroup. Second, we examined perceptions of intergroup threat as an additional outcome variable to test whether more inclusive identities were associated with this more distal outcome. Perceptions of intergroup threat play an important role in shaping intergroup relations \parencite[for a review, see][]{nelson_intergroup_2016}. We examined whether participants who included caste and religious minorities in their ingroup would, in addition to feeling more warmth and less social distance toward them, feel less threatened by them in terms of both realistic and symbolic threat. As we had not planned our study with clear directional predictions concerning social dominance orientation and intergroup threat, we consider these additional analyses exploratory.

\section{Method}

All materials, data, analysis scripts, and appendices are available online.\footnote{\protect\href{https://doi.org/10.17605/OSF.IO/QPCRM}{https://doi.org/10.17605/OSF.IO/QPCRM}} Here, we only report measures testing our hypotheses, omitting measures replicating earlier research or validating the experimental task (Appendix A). Reanalysing existing data \parencite{van_dommelen_construing_2015}, we determined that $\sim 100$ respondents per group would allow reasonably precise estimates of model parameters (Appendix B). We report descriptive statistics and correlations in Appendix C.

\subsection{Participants}

We recruited 351 students at Karnatak University (Dharwad, India). Of these, we excluded 49 participants who did not belong to any of four caste groups (n = 20), failed to indicate their caste group ($n = 7$), and/or reported Islam as their own or their family’s religion ($n = 27$).\footnote{Because Muslims---unlike Jains and Christians---featured in the experimental task, we would have had to consider them as a distinct group in the analyses. As this subsample was too small for any meaningful analyses, we instead opted to exclude Muslim participants.} This left 302 participants who reported Hinduism ($n = 286$), Jainism ($n = 8$), or Christianity ($n = 8$) as their or their family’s religion, and General Caste ($n = 99$), Other Backward Class ($n = 127$), Scheduled Caste ($n = 54$), or Scheduled Tribe ($n = 22$) as their caste group. Table~\ref{tab:t1} summarizes participants by gender, age, nationality, religion, and caste.

\begin{table}    
\caption{Participants by gender, age, nationality, religion, and caste. Categories in \textit{italics} were excluded from the final sample. N/A marks missing responses.}
\centering
\figureversion{lining, tabular}
\small	
\begin{tabular}{llrr} \addlinespace \toprule
\multicolumn{2}{l}{Category} & $n$ & \% \\ \midrule \addlinespace 
Gender      & Woman      & 215 & 61 \\
            & Man & 121 & 34 \\
            & Other & 0 & 0 \\
            & N/A & 15 & 4 \\ \addlinespace \addlinespace
Age         & 18--20 & 1 & 0 \\
            & 21--23 & 254 & 72 \\
            & 24--26 &  77 & 22 \\
            & 27--29 &  10 &  3 \\
            & 30--32 &   1 &  0 \\
            & 33--35 &   0 &  0 \\
            & 36 or older & 1 & 0 \\ 
            & N/A & 7 & 2 \\ \addlinespace \addlinespace
Nationality & Indian & 339 & 97 \\
            & Other & 0 & 0 \\
            & N/A & 12 & 3 \\ \addlinespace \addlinespace
Religion    & Buddhism & 1 & 0 \\ 
            & Christianity & 11 & 3 \\ 
            & Hinduism & 297 & 85 \\ 
            & \textit{Islam} & \textit{27} & \textit{8} \\ 
            & Jainism & 8 & 2 \\ 
            & Other & 2 & 1 \\ 
            & N/A & 5 & 1 \\ \addlinespace \addlinespace
Caste       & General Caste & 104 & 30 \\ 
            & Other Backward Class & 143 & 41 \\ 
            & Scheduled Caste & 54 & 15 \\ 
            & Scheduled Tribe & 23 & 7 \\ 
            & \textit{Other / Not applicable} & \textit{20} & \textit{6} \\ 
            & \textit{N/A} & \textit{7} & \textit{2} \\ \addlinespace \midrule
Total       &   & 351 & 100 \\ \bottomrule
\end{tabular}
\label{tab:t1}
\end{table}

\subsection{Procedure}

Participants completed a triple crossed-categorization task, in which they viewed 24 identity cards. Each showed a fictitious person’s name, age, religion, nationality, caste reservation, and a head-and-shoulders silhouette. Based on a pilot study, we manipulated the target’s caste, religion, and nationality such that each target represented a person with whom participants shared none, one, two, or three group memberships (Figure~\ref{fig:f2}). We tested participants in classrooms of 24--71 students by presenting targets in a slide-based presentation and by handing each student a pen-and-paper questionnaire. Each slide contained a male and a female target with participants focusing on the target corresponding to their gender. Slides also contained a number identifying each target, and response scale(s) corresponding to the question(s) participants answered at the time.

\begin{figure}
\caption{Examples of targets used in the triple crossed-categorization task}
\centering
\includegraphics[scale=1]{../figures/figure-2}
\caption*{\textit{Note.} Based on ratings in a pilot study ($N = 26$), we selected the four most prototypical targets (out of fifty initial targets) for each of six plausible combinations of caste, religion, and nationality (for details, see Appendix~D). Each target showed a person's caste reservation (GM = General Merit, OBC = Other Backward Class, SC/ST = Scheduled Caste/Scheduled Tribe), religion (Hindu, Muslim), and nationality (Indian, Nepali, Sri Lankan, Bangladeshi). Each target also showed the person's first and last name, age (21--26 years), and a silhouette corresponding to the person's gender \protect\parencite[adapted from][]{ma_chicago_2015}. Each target's age and silhouette, as well as the order in which the targets were presented, varied across sessions.}
\label{fig:f2}
\end{figure}

In each session, participants first familiarized themselves with each target (shown for 7 s in a randomized order) in an automated slide show. Participants viewed targets (in the same order) for a second time, noting for each target whether they felt that this person was one of their own group (1 = “us”), or not one of their own group (0 = “not us”). Participants viewed targets for a third time, rating how comfortable or uncomfortable they would feel to share a room with this person (social distance; 1 = \textit{very uncomfortable}, 7 = \textit{very comfortable}), and how they felt toward this person (feeling thermometer; 0 = \textit{cold}, 100 = \textit{warm}). Participants then completed the measures described below.

\subsection{Measures}

We report one of two reliability indices for our measures, the Spearman-Brown statistic ($\rho$) for two-item measures \parencite{eisinga_reliability_2013} and McDonald’s omega ($\omega$) for multi-item measures \parencite{dunn_alpha_2014}.

We measured intergroup contact as: how often, from 1 = \textit{never} to 5 = \textit{very often,} participants meet outgroup members in their everyday life (contact quantity), and how often, on average, they have positive/good contact and negative/bad contact with outgroup members \parencite{barlow_contact_2012}. We preceded these items with examples of positive and negative contact experiences. We measured cross-group friendship with two items \parencite{turner_reducing_2007}: “How many close friends do you have who are [outgroup members]?” (1 = \textit{none}, 5 = \textit{more than ten}), and “How often do you spend time with [outgroup] friends?” (1 = \textit{never} to 5 = \textit{very often}; $.65 < \rho < .71$). Participants reported contact with four groups: Dalits, people from other backward classes, people from general castes, and Muslims.

We measured social dominance orientation as how much, between 1 = \textit{strongly oppose }and 7 = \textit{strongly favour}, participants endorsed eight statements about social hierarchies \parencite{ho_nature_2015}. Four items measured support for group-based dominance (SDO-Dominance), for example, “some groups of people are simply inferior to other groups”. Four items measured opposition to egalitarian ideologies (SDO-Egalitarianism), for example, “it is unjust to try to make groups equal”.\footnote{Replicating \protect\textcite['s][]{ho_nature_2015} findings, we found a four-factor model (with two method factors) to represent the data better than the one-factor ($\Delta\chi^2 = 155.14, p < .001$) or two-factor ($\Delta\chi^2 = 138.67, p < .001$) alternatives. Accounting for this structure, we used latent factor scores for SDO-Dominance and SDO-Egalitarianism in our analyses.}

We measured realistic threat---from Muslims and Dalits---with three items per outgroup \parencite{schmid_reducing_2014}, e.g., “the more power [Muslims/Dalits] gain in this country, the more difficult it is for [Hindus/people from my caste group]” (1 = \textit{strongly disagree}, 5 = \textit{strongly agree}; $\omega_\textit{Muslims} = .71, \omega_\textit{Dalits} = .79$). Two items measured symbolic threat, e.g., “[Muslims/Dalits] threaten [Hindus’/my caste group’s] way of life” (1 = \textit{strongly disagree}, 5 = \textit{strongly agree}; $\rho_\textit{Muslims} = .61, \rho_\textit{Dalits} = .65$).

We measured perceived (dis-)advantage as how easy or hard participants thought it was, on average, for people from various groups to succeed in India today (1 = \textit{very hard}, 7 = \textit{very easy}). Participants rated seven groups: People from your own background, Scheduled Caste, Scheduled Tribe, Other Backward Class, General Caste, Hindus, and Muslims.

Five items measured policy support. Participants read that “currently, 22.5\% of seats in central-government funded universities are reserved for Scheduled Caste and Scheduled Tribe students”, and that “an additional 27.5\% of seats in central-government funded universities are reserved for students from Other Backward Classes”. Participants indicated to what extent they opposed or supported reservation in higher education for students from each group (1 = \textit{strongly oppose}, 5 = \textit{strongly support}), and whether they thought that reservation in higher education for students from that group should increase, decrease, or remain unchanged (1 = \textit{decrease a lot}, 5 = \textit{increase a lot}; $\rho_\text{SC/ST} = .80, \rho_\text{OBC} = .80$). Participants then read that “no seats in central-government funded universities are reserved for Muslim students nationally, though some states have introduced quotas for Muslim students”. Participants indicated to what extent they opposed or supported reservation for Muslim students.

\subsection{Analysis strategy}

To answer our research questions, we used various (generalized) linear regression models. Specifically, we examined: (1) \emph{group} and \emph{individual differences} in how likely participants were to categorize different targets as “us” in a series of multilevel logistic models with participants’ target categorizations (1 = “us”, 0 = “not us”) as outcome variable; (2) consequences of participants’ target categorizations for \emph{intergroup attitudes} in a series of multilevel multivariate linear models with participants’ target-wise social distance and feeling thermometer ratings as outcome variables; and (3) consequences for \emph{support for social change} in a series of multivariate linear models with participants’ group-wise perceived (dis-)advantage and policy support ratings as outcome variables. We also explored whether participants’ target categorizations were associated with their intergroup threat ratings using multilevel linear models.

We estimated models in RStan \parencite{stan_development_team_rstan:_2020} using Bayes\-ian statistical methods. Bayesian inference involves choosing a likelihood function and prior distributions. The likelihood function links the observed data to one or more model parameters (e.g., regression coefficients) and states how likely the observed data are given different values of said model parameters. Our models derived the likelihood of the observed responses from a generalized linear model with a logit link function or a linear model with a (multivariate) normal distribution. Prior distributions state how plausible different values of said model parameters are before considering the observed data. Our models assigned conservative, weakly informative prior distributions to all model parameters \parencite{gelman_prior_2017}.\footnote{Specifically, we used $\beta \sim \text{Student-t}(2.5, 0, 1)$ for fixed effects in logistic models, $\beta \sim \text{Normal}(0, 1)$ for fixed effects in linear models, $\Omega \sim \text{LKJ}(4)$ for residual covariances in multivariate models, and $\sigma \sim \text{Half-Cauchy}(0, 1)$ for standard deviations of varying effects in multilevel models and for residual standard deviations in linear models.} Bayesian inference applies Bayes’ theorem to update prior distributions in light of the observed data to produce posterior distributions.\footnote{For a detailed introduction, consult \textcite{gelman_bayesian_2014}, \textcite{lambert_students_2018}, and \textcite{mcelreath_statistical_2016}.} Other than \textit{p}-values and confidence intervals, the resulting posterior distributions have a straight-forward interpretation as stating how plausible different values of the model parameters are given the observed data.

We tested our hypotheses in two steps. First, we compared models that corresponded to our hypotheses and selected the model that made the most accurate predictions. For example, we compared a model which estimated the probability of participants’ categorizing a target as “us” in the experimental task as \emph{varying} across the participants’ group memberships to a simpler model which constrained this probability to be \emph{fixed} across the participants’ group memberships. When the former made more accurate predictions than the latter, we considered this evidence that, as hypothesized, participants from advantaged and disadvantaged groups differed in how likely they were to categorize targets as “us”. Second, we inspected estimates from the selected model to examine whether model estimates were in the hypothesized direction. For example, we found that, as hypothesized, the selected model estimated advantaged-group participants to be less likely than disadvantaged-group participants to categorize disadvantaged-group targets as “us” ($\Pr = .80, [.73, .85]$ versus $\Pr =  .97, [.95, .98]$; $\Delta\Pr =  -.17, [-.23, -.12]$). For each model estimate, we report a point estimate and an uncertainty interval enclosing the 97\% most plausible estimates.
